Expectations, Outcomes, and Challenges \\ of Modern Code Review

### 2013-03-01 sections/introduction.tex
removed sentence about a thing we do not actually do

Nowadays many organizations are adopting more lightweight code review
practices to limit the inefficiencies of inspections. In particular, there is a
clear trend toward the usage of tools developed to support code
review~\cite{rigby2012open}. In the context of this paper, we define
\emph{Modern Code Review}, as review that is \begin{inparaenum}[(1)]
\item informal (in contrast to Fagan-style), 
\item tool-based, and that 
\item occurs regularly in practice nowadays, for example at companies such as Microsoft, Google~\cite{kennedy2006online},
Facebook~\cite{tsotsis2011online}, and in other companies and OSS projects~\cite{gerrit2012online}. \end{inparaenum}

This trend raises questions, such as: Can we apply the lessons learned from
previous research on code inspections to modern code reviews? What are the
expectations for code review nowadays? What are the actual outcomes of code
review? What challenges do people face in code review?

>>>>

Nowadays many organizations are adopting more lightweight code review
practices to limit the inefficiencies of inspections. In particular, there is a
clear trend toward the usage of tools developed to support code
review~\cite{rigby2012open}. In the context of this paper, we define
\emph{Modern Code Review}, as review that is \begin{inparaenum}[(1)]
\item informal (in contrast to Fagan-style), 
\item tool-based, and that 
\item occurs regularly in practice nowadays, for example at companies such as Microsoft, Google~\cite{kennedy2006online},
Facebook~\cite{tsotsis2011online}, and in other organizations and OSS projects~\cite{gerrit2012online}. \end{inparaenum}

This trend raises questions, such as: What are the
expectations for code review nowadays? What are the actual outcomes of code
review? What challenges do people face in code review?
